\textbf{Efficient Implementation Strategies for Block Ciphers on ARMv8}\\ {\footnotesize Bachelorarbeit}

### 2023-03-06 Paper/paper.tex
shl/shr for vec registers

Bitslicing refers to the technique of splitting up $n$ bits into $m$ slices to
achieve a more efficient representation to operate on. The structure of
\texttt{GIFT} naturally offers possibilities for bitslicing. We split the
cipher state bits $b_{63}b_{62}\dots b_0$ into four slices $S_i,
i\in\{0,1,2,3\}$ such that the $i$-th slice contains all $i$-th bits of the
individual S-boxes.

@@

Let $a,b,c,d,e,f,g,h$ be eight messages with subscripts denoting individual
bits. We first put these messages into four SIMD registers $V_0,V_1,V_2,V_3$:

@@

@@

\section{Limitations}

\section{Benchmarks}

>>>>

Bitslicing refers to the technique of splitting up $n$ bits into $m$ slices to
achieve a more efficient representation to operate on. The structure of
\texttt{GIFT} naturally offers possibilities for bitslicing. We split the
cipher state bits $b_{63}b_{62}\dots b_0$ into four slices $S_i,
i\in\{0,1,2,3\}$ such that the $i$-th slice contains all $i$-th bits of the
individual S-boxes. This is equivalent to transposing the bit matrix.

@@

Let $a,b,c,d,e,f,g,h$ be eight messages of length $64$ with subscripts denoting
individual bits. We first put these messages into four SIMD registers
$V_0,V_1,V_2,V_3$:

@@

We will provide implementations for the presented strategies in the C
programming language. Although directly writing Assembler code could result in
a small performance benefit, this generally increases the work necessary by an
order of magnitude for only limited results.

@@
